GRN inference in multiple species

### 2015-04-29 paper1.tex
added figs

@@

\subsection{Optimization and model selection}

@@

@@

As expected, increasing the weight of the fusion constraint $\lambda_S$ improved network recovery. Networks with higher orthology coverage saw a greater benefit from fusion, although the improvement was not limited to analogous interactions. One way of assessing the effect of fusion on network inference performance is to compute an ``exchange-rate'' between conditions in each network. Suppose you are interested in determining a regulatory network for species A, a model organism which is experimentally inconvenient. A related species, B, is easier to collect data for, but of less intrinsic interest. Our simulation results suggest that adding conditions from species B to a fused network inference problem has an effect on network A recovery that is similar to adding conditions from A at a reduced rate.

@@

\subsection{Fused regression improves performance on both the constrained and non-constrained parts of the network}
We wanted to know if using fused regression on networks with only conserved subgraphs affected the recovery of the non constrained parts of the networks. We used sets of two networks with 20 TFs and 200 genes each, where each set had 0\%, 25\%, 50\%, or 75\% of the TFs and genes in orthology groups. We varied lamS and computed AUPR using cross-validation on the portion of the network that had fusion constraints, the portion without any orthology information, and on the whole network. On the fused networks, performance improved as the fusion penalty weight increased; interestingly, performance gains are seen even the portion of the network where no orthology information is known. By constraining part of an underdetermined system, we obtain gains in both parts.

@@

We performanced a simulation to assess the ability of our adaptive fusion algorithm to learn which parts of two input networks are conserved when orthology information is faulty. We generated synthetic fused networks and introduce error in the fusion constraints by adding false positives and negatives to the orthology information given to the solver. Because we know which entries in the orthology mapping are ``fake'' (not reflected in the generation of the networks), we can label fusion constraints that involve one or more ``fake'' mappings as being ``fake''. We verified that adaptive-fusion unfused mostly ``fake'' interactions, while leaving truly analogous interactions fused.

\subsection{SCAD improves network inference}
We wanted to determine whether SCAD is able to improve learning of GRNs. That is, beyond correctly identifying functional conservation and recovering the performance lost by fusing neofunctionalized genes, is our method able to produce more accurate networks than those learned without fusion?

>>>>

\subsection{Model selection}

@@

\subsection{Optimization}

@@

\begin{figure}
\begin{center}
  \includegraphics[scale=0.45]{l2fusionquick.png}
  \caption{\label{fig:figure1} The x-axis represents lamS and the y-axis represents the proportion of nodes which are orthologous. As the networks increase in similarity, performance improves and benefits from a large fusion penalty weight}
  \end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[scale=0.45]{increase_data2.png}
  \caption{\label{fig:figure1} We fuse two networks, using lamS=0 and nonzero lamS, and hold the number of conditions in network 1 constant while varying the number of data points for network 2. We plot the performance of network 2.}
  \end{center}
\end{figure}

@@

As expected, increasing the weight of the fusion constraint $\lambda_S$ improved network recovery (Figure 2). Networks with higher orthology coverage saw a greater benefit from fusion, although the improvement was not limited to analogous interactions. One way of assessing the effect of fusion on network inference performance is to compute an ``exchange-rate'' between conditions in each network. Suppose you are interested in determining a regulatory network for species A, a model organism which is experimentally inconvenient. A related species, B, is easier to collect data for, but of less intrinsic interest. Our simulation results suggest that adding conditions from species B to a fused network inference problem has an effect on network A recovery that is similar to adding conditions from A at a reduced rate (Figure 3).

@@

\begin{figure}
\begin{center}
  \includegraphics[scale=0.45]{con_noncon.png}
  \caption{\label{fig:figure4} We looked at four different sets of networks, where each set had different amounts of orthologous genes. We plotted the performance on the whole network, the constrained, and non-constrained portions of the network as we increased the fusion penalty weight.}
  \end{center}
\end{figure}

\subsection{Fused regression improves performance on both the constrained and non-constrained parts of the network}
We wanted to know if using fused regression on networks with only conserved subgraphs affected the recovery of the non constrained parts of the networks (Figure 4). We used sets of two networks with 20 TFs and 200 genes each, where each set had 0\%, 25\%, 50\%, or 75\% of the TFs and genes in orthology groups. We varied lamS and computed AUPR using cross-validation on the portion of the network that had fusion constraints, the portion without any orthology information, and on the whole network. On the fused networks, performance improved as the fusion penalty weight increased; interestingly, performance gains are seen even the portion of the network where no orthology information is known. By constraining part of an underdetermined system, we obtain gains in both parts.

\begin{figure}
\begin{center}
  \includegraphics[scale=0.45]{plot_betas_scad_l2.png}
  \caption{\label{fig:figure1} This is what a figure looks like}
  \end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[scale=0.45]{plot_betas_scad.png}
  \caption{\label{fig:figure1} This is what a figure looks like}
  \end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[scale=0.45]{scadf.png}
  \caption{\label{fig:figure1} This is what a figure looks like}
  \end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[scale=0.45]{scadt.png}
  \caption{\label{fig:figure1} This is what a figure looks like}
  \end{center}
\end{figure}

@@

We performanced a simulation to assess the ability of our adaptive fusion algorithm to learn which parts of two input networks are conserved when orthology information is faulty (Figure 5-8). We generated synthetic fused networks and introduce error in the fusion constraints by adding false positives and negatives to the orthology information given to the solver. Because we know which entries in the orthology mapping are ``fake'' (not reflected in the generation of the networks), we can label fusion constraints that involve one or more ``fake'' mappings as being ``fake''. We verified that adaptive-fusion unfused mostly ``fake'' interactions, while leaving truly analogous interactions fused.

\begin{figure}
\begin{center}
  \includegraphics[scale=0.45]{test_scad_opt_params3.png}
  \caption{\label{fig:figure1} This is what a figure looks like}
  \end{center}
\end{figure}

\subsection{SCAD improves network inference}
We wanted to determine whether SCAD is able to improve learning of GRNs. That is, beyond correctly identifying functional conservation and recovering the performance lost by fusing neofunctionalized genes, is our method able to produce more accurate networks than those learned without fusion? (Figure 9)
